\section{Conclusion and Future Plan}
\subsection{Conclusion}
After two months’ effort of all our 8 members, we successfully build this health center, with both front-end and back-end side developed by ourselves.  Our team mainly focus on how to make the website practical and secure.

To make the system practical, we put a lot of thoughts on how make a coherent and streamlined process and implementation details. For example, we did pattern validation, passed a fresh appointment to doctor’s page, etc. 

Considering that there are many sensitive information stored in hospital, we tried our best to make the website. We implemented a log table and managed to avoid many potential security problems. Consequently, the website is easy to maintain and difficult to attack.

Though we had thought of creating a role for patients, we decided not to include it after consideration. We designed this website for hospital internal use, and whatever patients want to do can be done with reception’s assistance. Moreover, adding a patient role may greatly increase the attack surface of our website.

\subsection{Future Plan}
\begin{enumerate}
    \item Complete password hashing. 
    
This is an important fail safe strategy. If only hash values of passwords of users are stored in our database, attackers will never know the actual passwords of users. We are about to finish it!
    \item Improve health history management
For now, all doctors can view all health history. We are planning to make doctors only able to view health histories related to him. The less privilege, the better! :)

\end{enumerate}

\newpage 
\section*{Thanks to Dr. Yu and TAs!}