\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{float}

\title{Syracuse Hospital Management System\\
\large A secure and practical design\vspace{5cm}}
\author{Ziqi Wang\and Xiaojun Zhang \and Yufei Fang \and Yue Zhao \and Chenyang Du \and	Huiyuan Li \and Hanyi Li \and Haiyang Zhang }
\date{May 2018}
\begin{document}

\maketitle
\newpage
\tableofcontents
\newpage

\begin{abstract}
    Computer science continues to develop, to provide a great convenience to various fields. At present, the patients become more and more and medical institutions accounts more and more miscellaneous. Therefore, it is necessary to develop an electronic Hospital Management Information Systems with a simple, convenient, high reliability, high storage capacity, high security, long time preservation, and low cost. 
    
    This report firstly introduces development significance of the development of electronic medical record system and related technology. Then the system design tasks and detailed design methods are analyzed according to the needs, and focuses on the database structure design, and the main function modules of the real and related functions. Finally, it summarizes the system’s functional characteristics, the existing problems, and the corresponding improvement program. This system mainly uses the current relatively popular in the JSP to develop, adopt suitable for small to medium sized projects the MySQL database. The system is mainly divided into three functional modules: user management module, patient management module and the warehouse management module, according to the different roles to show the corresponding menu, the main functions of the system have a personnel management, records management, warehouse management, and log view, etc.
\end{abstract}
\newpage
\input{intro.tex}
\input{dev.tex}
\input{sys.tex}
\input{database.tex}
\input{implement.tex}
\input{sec.tex}
\input{evaluation.tex}
\input{conclusion.tex}


\end{document}
